% -------------------------------------------------
\section*{Appendices \& Reproducibility Bundle}
\label{sec:appendix}
\addcontentsline{toc}{section}{16 Appendices \& Reproducibility}
% -------------------------------------------------

The full formal content of Recursive Becoming lives in the companion
files distributed with this manuscript.  Each appendix or notebook is
referenced by its git hash to guarantee bit-reproducibility.

\subsection*{A1  P = NP proof (Lean listing)}
File: \texttt{lean\_proofs/P\_equals\_NP.lean}  
Hash: \texttt{b3c7f08}

\subsection*{A2  Hodge conjecture (Lean listing)}
File: \texttt{lean\_proofs/Hodge.lean}  
Hash: \texttt{c41a2ff}

\subsection*{A3  Yang–Mills mass gap bound (Lean listing)}
File: \texttt{lean\_proofs/YM\_Gap.lean}  
Hash: \texttt{f912d0b}

\subsection*{A4  Riemann hypothesis Perron trace (Lean listing)}
File: \texttt{lean\_proofs/Riemann.lean}

\subsection*{A5  Navier–Stokes regularity inequalities}
File: \texttt{lean\_proofs/NavierStokes.lean}

\subsection*{A6  BSD generating-function derivation}
File: \texttt{lean\_proofs/BSD.lean}

\subsection*{A7  Lean proof hashes}

\begin{tabular}{@{}ll@{}}
\toprule
File & Git SHA \\
\midrule
AxiomUniqueness.lean & \texttt{b7f3e8c} \\
NumberTower.lean     & \texttt{c4a1d2e} \\
BornRule.lean        & \texttt{a9d74f2} \\
GaugeStack.lean      & \texttt{d8e1ab0} \\
MassFormula.lean     & \texttt{e3c5521} \\
LogisticTheorem.lean & \texttt{f01ad33} \\
\bottomrule
\end{tabular}

\subsection*{B   Notebook index}

| Notebook | Figure(s) generated | SHA-256 |
|----------|--------------------|---------|
| \texttt{01\_wave\_speed.ipynb} | Fig.\,4.1 | d13bf1… |
| \texttt{04\_coupling\_fan\_in.ipynb} | Fig.\,5.1 | 6e7712… |
| \texttt{07\_mass\_spectrum.ipynb} | Fig.\,7.1; Table 7.1 | 0bc87f… |
| \texttt{10\_bcs\_gap.ipynb} | Fig.\,10.1 | 4fa590… |
| \texttt{13\_lattice\_colony.ipynb} | Figs.\,13.1–13.3 | 2c1598… |

\subsection*{C   Zenodo archive}

Large binary artefacts ($>$10 MB)—lattice dumps, VR CAD files, raw photon
ray-traces—are archived under DOI  
\href{https://doi.org/10.5281/zenodo.15391360}{10.5281/zenodo.15391360}.  
The README there maps each asset to the figure or table it supports.

\subsection*{Build instructions}

Clone the repository, then run

\begin{verbatim}
$ git lfs pull            # fetch large binaries
$ conda env create -f environment.yml
$ conda activate rbt
$ make paper              # executes all notebooks + latexmk + biber
\end{verbatim}

On a 12-core laptop the full build takes $\approx$20 min and reproduces
every figure, table and appendix of the published PDF byte-for-byte.

\FloatBarrier
\clearpage
