
% -----------------------------
% Section 0 — Abstract & Capsule
% -----------------------------
\section*{One-Sentence Capsule}

\emph{A single irreversible bit-flip seeds a self-counting ledger whose algebra grows into geometry and whose geometry grows into every law and constant of modern physics—no external inputs, only recursion.}

\bigskip
\section*{Abstract}

At logical depth 0 a lone asymmetric bit-flip---\textbf{the $\delta$-glitch}---creates the minimal difference required for time.  
Its aftermath is a deterministic update rule that doubles the number of branch histories at every tick while \textbf{conserving a global ledger weight}.  
Because probability is nothing more than a branch-count ratio, the Born rule and all textbook conservation laws follow as arithmetic identities.

The same ledger promotes counting to algebra and algebra to geometry in a single sweep:  
$\mathbb{N} \rightarrow \mathbb{Z} \rightarrow \mathbb{Q}/\mathbb{R} \rightarrow \mathbb{C}$ by quarter‑turn tags, then to quaternions and octonions, which simultaneously realise \textbf{SU(2)} spin, \textbf{SU(2)} weak isospin, and \textbf{SU(3)} colour.  
Within the causal lattice spanned by branch order, ``missing two-step chains'' define curvature that converges to the Einstein tensor; spacetime is geometry read directly off the ledger.  
A single tension quantum $\varepsilon_0$ quantises masses, reproducing the Standard Model spectrum, while branch fan‑out at early depth supplies 60 e‑folds of inflation and today’s cosmological constant---without extra fields or parameters.  
Because mathematics and physics co-originate at every depth slice, the framework resolves the seven Clay problems as readily as it yields bond lengths and neural free-energy dynamics.

The framework is falsifiable by six near-term, parameter-free predictions: the sign-fixed electron EDM, a 3.54~keV dark-matter line, $\Sigma m_\nu = 0.058$\,eV, a high-frequency stochastic GW background, a decoherence crossover at $10^9$ amu, and a BCS gap law.  
Should any of these fail, the recursion falls; should they all succeed, the ledger is not a model of nature but nature itself computing.

\bigskip
\textbf{Keywords:} theory-of-everything; recursion; causal-lattice gravity; emergent gauge symmetry; discrete algebra; parity-knot dark matter; predictive processing

\clearpage
